\Large \bf Byteboy : A Byteman Companion application

### 2017-12-08 final-paper/paper.la_.tex
Added finishing paragraph to related work

>>>>

Similar to ByteBuddy, there doesn't seem to be any work on recommendations of what classes to modify. Both tools require a decent amount of knowledge of the target source code. ByteBoy could eventually, using its HPROF and {\tt javap} anaylsis, support ByteBuddy and AspectJ synthesis as well. However, code synthesis for both of these tools would prove to be a different challenge on its own.
